Make any stupid plot you want

### 2021-01-27 draft/sections/math.tex
compiles again after lost }

\section{Topological Artist Model}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/dar.png}
    \caption{Visualizaiton is the process of converting data into visual characteristics that are then assembled into a graphic}
    \label{fig:artist_stages}
\end{figure}

\note{can change this all to 3rd person passive later}\\
%% add sentence or two about visualization as structure preserving map
In this section we introduce a mathematical description of the visualization pipeline where artist $\mathscr{A}$ functions transform data space $\mathscr{E}$ to an intermediate representation in a prerendered graphic space $\mathscr{H}$.

@@

\begin{figure}[ht!]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
        %% add box around neighboring P and Map
        \caption{}
        \label{fig:base_example_discrete}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2k.png}
        \caption{}
        \label{fig:base_example_continuous}
    \end{subfigure}
    \caption{These two datasets have the same (time, temperature) fiber. In figure~\ref{fig:base_example_line} the total space $E$ is discrete over points $k \in K$, meaning the records in the fiber are also discrete. In figure~\ref{fig:base_example_plane} $E$ lies over the continuous interval $K$, meaning the records in the fiber are sampled from a continous space. 
    \note{revamp figure: F=Plane, k1 = dots, k2=line}}
    \label{fig:base_example}
\end{figure}

@@

\begin{figure}[ht!]
    \includegraphics[width=.5\linewidth]{figures/math/fiberbundle.png}
    \caption{ Fiber (time, temperature) with an interval $K$ basespace. The sections $\tau_1$ and $\tau_2$ are constrained such that the time variable must be monotonic, which means each section is a timeseries of temperature values. They are included in the global set of sections  $\tau_1, \tau_2 \in \Gamma(E)$}
    \label{fig:data_sections}
\end{figure}

@@

\subsection{Artist}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/path_of_q}

@@

\subsubsection {Visual Fiber Bundle $V$}
The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels,} in fiber $P$. The fiber space $P$ is defined in terms of the parameters of the visualization specification and the values those parameters resolve to - for example ggplot \cite{wickhamGgplot2ElegantGraphics2016a}, D3\cite{bostockDataDrivenDocuments2011
\begin{table}[H]
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $\{f_{0}, \ldots, f_{n}\} \times (\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
    \caption{Some possible components of the fiber $P$ for a visualization implemented in Matplotlib}
    \label{tab:mpl_visual_variable_fiber}
\end{table}

>>>>

\section{Topological Artist Model}
\label{sec:tam}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/dar.png}
    \caption{Visualizaiton is the process of mapping data into visual characteristics that are then assembled into a graphic}
    \label{fig:artist_stages}
\end{figure}

\note{can change this all to 3rd person passive later}\\
Visualization is generally thought of as structure preserving maps from data into graphics, and in this section we formally define that structure and how it is preserved via equivariant maps. We can then specify that a faithful visual mapping is structure preserving, and apply these constraints to visualizations we may want to develop or implement. We model the data, visual characteristic, and graphic stages of visualization, shown in figure~\ref{fig:artist_stages}, as topological structures that encapsulate types of variables and continuity; by doing so we can develop implementations that keep track of both in ways that let us distribute computation while still allowing assembly and dynamic update of the graphic.

We introduce a mathematical description of the visualization pipeline where artist $\mathscr{A}$ functions transform data space $\mathscr{E}$ to an intermediate representation in a prerendered graphic space $\mathscr{H}$.

@@

\begin{figure}[ht!]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
        %% add box around neighboring P and Map
        \caption{}
        \label{fig:base_example_discrete}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2k.png}
        \caption{}
        \label{fig:base_example_continuous}
    \end{subfigure}
    \caption{These two datasets have the same (time, temperature) fiber. In figure~\ref{fig:base_example_line} the total space $E$ is discrete over points $k \in K$, meaning the records in the fiber are also discrete. In figure~\ref{fig:base_example_plane} $E$ lies over the continuous interval $K$, meaning the records in the fiber are sampled from a continuous space. 
    \note{revamp figure: F=Plane, k1 = dots, k2=line}}
    \label{fig:base_example}
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=.5\linewidth]{figures/math/fiberbundle.png}
    \caption{ Fiber (time, temperature) with an interval $K$ basespace. The sections $\tau_1$ and $\tau_2$ are constrained such that the time variable must be monotonic, which means each section is a timeseries of temperature values. They are included in the global set of sections  $\tau_1, \tau_2 \in \Gamma(E)$}
    \label{fig:data_sections}
\end{figure}

@@

\subsection{Artist}
\label{sec:artist}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/path_of_q}

@@

\subsubsection {Visual Fiber Bundle $V$}
The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels} in fiber $P$. The fiber space $P$ is defined in terms of the parameters of the visualization specification and the values those parameters resolve to - for example ggplot \cite{wickhamGgplot2ElegantGraphics2016a} or D3\cite{bostockDataDrivenDocuments2011}.
\begin{table}[H]
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $\{f_{0}, \ldots, f_{n}\} \times (\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
    \caption{Some possible components of the fiber $P$ for a visualization implemented in Matplotlib}
    \label{tab:mpl_visual_variable_fiber}
\end{table}
